Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.Rmd
update exp design

@@

## Unknown

@@

(This section discu)

@@

>>>>

The effectiveness of lineup protocol has already been validated by @majumder_validation_2013 under relatively simple classical normal linear regression model settings with only one or two regressors. Their results suggest visual test is capable of testing the significance of a single regressor with a similar power as a t-test, though they expressed that in general it is unnecessary to use visual inference if there exists a conventional test and they didn't expect the visual test to perform equally well as the conventional test. In their third experiment, where there does not exist a proper conventional test, visual test outperforms the conventional test for a large margin. This is encouraging as it promotes the use of visual inference in border field of data science where there are no existing statistical testing procedures. In fact, lineup protocol has been integrated into some model diagnostic tools such as @loy2013diagnostic.

@@

(This section discusses the experimental design including the motivation of the experiment, an overview of the experiment, the simulation setting of the depatures from good residual plots, parameter choices, allocation of the lineups and other technical details.)

With our knowledge, the effectiveness of visual test relative to the equivalent conventional test in regression diagnostics has not been validated. Particularly, its ability to detect non-linearity and heteroskedasticity compared to model structural test and Breusch–Pagan test. Meanwhile, as mentioned in Section \ref{introduction} [introduction] section, we keen to understand the differences between conventional hypothesis testing and graphical diagnostics in the application of linear regression diagnostics and why conventional tests are not preferred by data analysts in linear regression diagnostics. Attempting to find the answer to these questions, three experiments were conducted.

The experiment I has ideal scenario for conventional testing, where the visual test is not expected to outperform the conventional test. The experiment II is a scenario where the conventional test is an approximate test, in which the visual test may have a chance to match the performance of the conventional test.

@@

@@

# Old stuff

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.tex
update exp design

\caption{\label{tab:example-residual-plot-table}Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are colored in red.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Residual plots & Departures & Model structural & Breusch-Pagan & Shapiro–Wilk\\
\midrule
B & Non-linearity & \textbf{0.000} & \textbf{0.000} & \textbf{0.039}\\
C & Heteroskedasticity & 0.378 & \textbf{0.000} & \textbf{0.000}\\
D & Non-normality & 0.667 & 0.736 & \textbf{0.000}\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

\hypertarget{unknown}{%
\subsection{Unknown}\label{unknown}}

@@

>>>>

\caption{\label{tab:example-residual-plot-table}Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are showed in bold.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Residual plots & Departures & Model structural & Breusch-Pagan & Shapiro–Wilk\\
\midrule
B & Non-linearity & \textbf{0.000} & \textbf{0.000} & \textbf{0.039}\\
C & Heteroskedasticity & 0.378 & \textbf{0.000} & \textbf{0.000}\\
D & Non-normality & 0.667 & 0.736 & \textbf{0.000}\\
\bottomrule
\end{tabular}
\end{table}

@@

The effectiveness of lineup protocol has already been validated by
\citet{majumder_validation_2013} under relatively simple classical
normal linear regression model settings with only one or two regressors.
Their results suggest visual test is capable of testing the significance
of a single regressor with a similar power as a t-test, though they
expressed that in general it is unnecessary to use visual inference if
there exists a conventional test and they didn't expect the visual test
to perform equally well as the conventional test. In their third
experiment, where there does not exist a proper conventional test,
visual test outperforms the conventional test for a large margin. This
is encouraging as it promotes the use of visual inference in border
field of data science where there are no existing statistical testing
procedures. In fact, lineup protocol has been integrated into some model
diagnostic tools such as \citet{loy2013diagnostic}.

@@

(This section discusses the experimental design including the motivation
of the experiment, an overview of the experiment, the simulation setting
of the depatures from good residual plots, parameter choices, allocation
of the lineups and other technical details.)

With our knowledge, the effectiveness of visual test relative to the
equivalent conventional test in regression diagnostics has not been
validated. Particularly, its ability to detect non-linearity and
heteroskedasticity compared to model structural test and Breusch--Pagan
test. Meanwhile, as mentioned in the \ref{introduction}
\protect\hyperlink{introduction}{introduction} section

For the purpose of investigating the differences between conventional
hypothesis testing and graphical diagnostics in the application of
linear regression diagnostics, three experiments were conducted.

The experiment I has ideal scenario for conventional testing, where the
visual test is not expected to outperform the conventional test. The
experiment II is a scenario where the conventional test is an
approximate test, in which the visual test may have a chance to match
the performance of the conventional test.

@@

\hypertarget{old-stuff}{%
\section{Old stuff}\label{old-stuff}}
